---
title: "labtools-vignette"
author: "The Gresham Lab"
date: "7/13/2020"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{labtools-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(labtools)
```

This vignette provides examples of how to use functions in the package *labtool*, which includes a set of useful functions developed in the [Gresham Lab](https://greshamlab.bio.nyu.edu/).

Available functions inlclude:

1. gff_from_snapgene_features()
2. hello()
3. std_err()
4. yeast_common_to_sgd()
5. yeast_common_to_systematic()
6. yeast_gene_names()
7. yeast_r64_to_systematic()
8. yeast_sgd_to_common()
9. yeast_sgd_to_systematic()
10. yeast_systematic_to_common()
11. yeast_systematic_to_sgd()

to install this package and vignette:

`library(devtools)`
`install_github("GreshamLab/labtools", build_vignettes = TRUE)`

to view vignette:

`help(package = 'labtools', help_type = 'html')`

or 

`vignette("labtool-vignette")`

## Below are some examples of how to use the functions and the expected output

### 1. How to make a gff from a snap gene file.

To run this example, download an example file (`SnapBarcodeLibrary1.csv`) from [here](https://drive.google.com/drive/folders/1Yrr3QSx4mJXIJmhNAc80astYtplfQGHZ?usp=sharing)

```{r}
make_gff_from_snap(file_path = "../../data/SnapBarcodeLibrary1.csv", chromosome = "II", feature_source = "levy_bc", output = "../../data/Barcode.gff")
```


The resulting gff (`Barcode.gff `) should be a plain text tab delimited file that looks like like this:

```{r}
file.show('../../data/Barcode.gff')
```

```
II	levy_bc	misc_feature	1001	1003	.	+	.	YBR209W
II	levy_bc	misc_feature	1004	1028	.	+	.	PEV9
II	levy_bc	misc_feature	1036	1514	.	+	.	GAL1 promoter
II	levy_bc	misc_feature	1611	2642	.	+	.	Cre
II	levy_bc	misc_feature	2133	2153	.	+	.	P23
II	levy_bc	misc_feature	2960	3211	.	+	.	CYC1 terminator
II	levy_bc	misc_feature	3220	3253	.	+	.	lox66/71
II	levy_bc	misc_feature	3233	3240	.	+	.	LoxP core
II	levy_bc	misc_feature	3262	3513	.	-	.	CYC1 terminator
II	levy_bc	misc_feature	3831	4057	.	-	.	Cre (truncated)
II	levy_bc	misc_feature	4088	4566	.	-	.	GAL1 promoter
II	levy_bc	misc_feature	7765	8715	.	-	.	HygMX
II	levy_bc	misc_feature	9174	9308	.	+	.	URA3 promoter
II	levy_bc	gene	9309	9497	.	+	.	URA3
II	levy_bc	misc_feature	9498	9503	.	+	.	Artificial Intron Start
II	levy_bc	misc_feature	9503	9527	.	+	.	Forward Sequencing Primer
II	levy_bc	misc_feature	9552	9577	.	+	.	BC2
II	levy_bc	misc_feature	9578	9611	.	+	.	loxP
II	levy_bc	misc_feature	9591	9598	.	+	.	loxP core
II	levy_bc	misc_feature	9612	9637	.	+	.	BC1
II	levy_bc	misc_feature	9646	9669	.	+	.	Reverse Sequencing Primer
II	levy_bc	misc_feature	9675	9681	.	+	.	Artificial intron branch point
II	levy_bc	misc_feature	9700	9702	.	+	.	Artificial intron terminator
II	levy_bc	misc_feature	9703	10317	.	+	.	URA3
II	levy_bc	misc_feature	10318	10394	.	+	.	URA3 terminator
II	levy_bc	gene	10754	11563	.	+	.	kanMX
II	levy_bc	misc_feature	11696	11715	.	+	.	NatMx
II	levy_bc	misc_feature	11696	11715	.	-	.	PEV8
II	levy_bc	misc_feature	11716	11718	.	+	.	YBR209W`
```

